\documentclass{amsart}
\usepackage[shortlabels]{enumitem}
\begin{document}

Some text in the document, not in the abstract\dots\footnote[1234567890]{It appears the point of this file is to write a very long footnote and see how the syncing performs. With the original (but messy) marking method, such a long footnote would not be a problem at all, other than if there is displayed text in the footnote and that text is selected by a PDF annotation. Like this:
\[
\sum\prod^n_{i = 0} \alpha_i .
\]
And an environment like a list inside a footnote isn't an issue either.
\begin{enumerate}[(i)]
\item here's one
\item and another
\item and the last
\end{enumerate}
Thankfully, though, you cannot put a figure in a footnote. You can, however, place a tabular.

\begin{tabular}{|c|c|}
\hline
why you would do this & I don't know \\
\hline
But if I had to bet, & would say that it has been done \\
\hline
\end{tabular}

Now to continue writing some text to pressure test the syncing (eventually for SyncTeX, anyway). Let's just write a good deal of text, why not? Let's go with some text from an arXiv paper.

The definition of an $\mathcal A_\infty$-coalgebra is less standardized in the literature than the definition of an $\mathcal A_\infty$-algebra. To be clear, for us an $\mathcal A_\infty$-coalgebra is a graded vector space $C$ and a degree $-1$ derivation of the \emph{completed} tensor algebra $\smash{\widehat T}(C[-1])$, which squares to zero. This amounts to a collection of maps
\[
\left\{ \Delta_n^C: C \longrightarrow C^{\otimes n} \right\}_{n \geq 1}~
\]
of degree $n-2$, which satisfy the relations imposed by the fact that the derivation that induces them squares to zero:
\[
\sum_{r+s+t = n}
(-1)^{\,r + s t}\,
\bigl(
\mathrm{id}^{\otimes r}
\otimes \Delta_s^C
\otimes \mathrm{id}^{\otimes t}
\bigr)
\circ \Delta_{\,r+1+t}^C
\;=\; 0,
\qquad n \ge 1 .
\]
A \emph{strict} morphism between two such coalgebras (as opposed to an $\infty$-morphism) is a homomorphism of graded vector spaces $f: C \longrightarrow C'$, with the property that the induced map $\smash{\widehat T}(C[-1]) \longrightarrow \smash{\widehat T}(C'[-1])$ is a homomorphism of dg algebras with respect to the differentials given by the respective derivations.}
\end{document}
