\documentclass{amsart}
\usepackage{hyperref}

%% \renewcommand{\eqref}[1]{(\ref{#1})}

\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

\begin{document}

\begin{equation}\label{eq}
  abc
\end{equation}

\begin{lemma}
\label{lem:cycle-optimality}
Fix a simple cycle $C$ and the feasible integer interval $[x_{\min},x_{\max}]$.
If each tier $p_{e,u}$ is nonincreasing in local liquidity, then $\Delta_C(x)$ is nonincreasing in $x$.
Consequently:
\begin{enumerate}
\item (\emph{Interior balance}) If there exists $x^\star\in[x_{\min},x_{\max}-1]$ with
\[
\Delta_C(x^\star)\ \ge\ 0\ \ge\ \Delta_C(x^\star\!+\!1),
\]
then every minimizer of $x\mapsto \Phi(\lambda_x)$ on $[x_{\min},x_{\max}]$ lies in $\{x^\star,x^\star\!+\!1\}\subset (x_{\min},x_{\max})$.
\item (\emph{Boundary depletion}) If no such sign change exists, then the minimizer is at a boundary:
$\arg\min \Phi(\lambda_x)=\{x_{\min}\}$ when $\Delta_C>0$ everywhere, and
$\arg\min \Phi(\lambda_x)=\{x_{\max}\}$ when $\Delta_C<0$ everywhere.
\end{enumerate}
\end{lemma}
{\it
  %% still run into italic correction issue when correction is inserted *before* the \markbox contents
  %% though I think italic corrections *before* are limited to italic parentheses

  (\emph{Boundary depletion})

  ( \emph{Boundary depletion})

  (\ \emph{Boundary depletion})    

  :\emph{Boundary depletion})
  
  : \emph{Boundary depletion})

  :\ \emph{Boundary depletion})    

  ;\emph{Boundary depletion})

  ; \emph{Boundary depletion})

  ;\ \emph{Boundary depletion})    

  ,\emph{Boundary depletion})

  , \emph{Boundary depletion})

  [\emph{Boundary depletion})

  [ \emph{Boundary depletion})

    [\ \emph{Boundary depletion})

      \{\emph{Boundary depletion})

      \{ \emph{Boundary depletion})

  \{\ \emph{Boundary depletion})                  

    }

    \vspace{24pt}

    \textsc{NOT IN ITALIC}

  (\emph{Boundary depletion})

  ( \emph{Boundary depletion})

  (\ \emph{Boundary depletion})    

  :\emph{Boundary depletion})
  
  : \emph{Boundary depletion})

  :\ \emph{Boundary depletion})    

  ;\emph{Boundary depletion})

  ; \emph{Boundary depletion})

  ;\ \emph{Boundary depletion})    

  ,\emph{Boundary depletion})

  , \emph{Boundary depletion})

  [\emph{Boundary depletion})

  [ \emph{Boundary depletion})

    [\ \emph{Boundary depletion})

      \{\emph{Boundary depletion})

      \{ \emph{Boundary depletion})

  \{\ \emph{Boundary depletion})                      

Equivalently, the expected cut width is nondecreasing in $k$ for \emph{every} fixed cut.

(1) \textit{stuff}; \emph{that}; \textbf{joins}. \textit{ourf}; $only$; \textsc{mission}.

(2) \textit{stuff;} \emph{that;} \textbf{joins.} \textit{ourf;} $only$; \textsc{mission.}

(3) \textit{stuff}\/; \emph{that}\/; \textbf{joins}\/. \textit{ourf}\/; $only$; \textsc{mission}\/.

(4) \textit{stuff}; \emph{that}; \textbf{joins}; \textit{ourf}; $only$; \textsc{mission}.

(5) \textit{stuff;} \emph{that;} \textbf{joins;} \textit{ourf;} $only$; \textsc{mission;}

(6) {\it stuff}; {\em that}; {\bf joins}; {\it ourf}; $only$; {\sc mission};

(7) {\it stuff;} {\em that;} {\bf joins;} {\it ourf;} $only$; {\sc mission;}

\vspace{12pt}

(1) \textit{stuff}, \emph{that}, \textbf{joins}. \textit{ourf}, $only$, \textsc{mission}.

(2) \textit{stuff,} \emph{that,} \textbf{joins.} \textit{ourf,} $only$, \textsc{mission.}

(3) \textit{stuff}\/, \emph{that}\/, \textbf{joins}\/. \textit{ourf}\/, $only$, \textsc{mission}\/.

(4) \textit{stuff}, \emph{that}, \textbf{joins}, \textit{ourf}, $only$, \textsc{mission}.

(5) \textit{stuff,} \emph{that,} \textbf{joins,} \textit{ourf,} $only$, \textsc{mission,}

(6) {\it stuff}, {\em that}, {\bf joins}, {\it ourf}, $only$, {\sc mission},

(7) {\it stuff,} {\em that,} {\bf joins,} {\it ourf,} $only$, {\sc mission,}

\vspace{12pt}

(1) \textit{stuff}. \emph{that}. \textbf{joins}. \textit{ourf}. $only$. \textsc{mission}.

(2) \textit{stuff.} \emph{that.} \textbf{joins.} \textit{ourf.} $only$. \textsc{mission.}

(3) \textit{stuff}\/. \emph{that}\/. \textbf{joins}\/. \textit{ourf}\/. $only$. \textsc{mission}\/.

(4) \textit{stuff}. \emph{that}. \textbf{joins}. \textit{ourf}. $only$. \textsc{mission}.

(5) \textit{stuff.} \emph{that.} \textbf{joins.} \textit{ourf.} $only$. \textsc{mission.}

(6) {\it stuff}. {\em that}. {\bf joins}. {\it ourf}. $only$. {\sc mission}.

(7) {\it stuff.} {\em that.} {\bf joins.} {\it ourf.} $only$. {\sc mission.}

\vspace{12pt}

(1) \textit{stuff}! \emph{that}! \textbf{joins}! \textit{ourf}! $only$! \textsc{mission}!

(2) \textit{stuff!} \emph{that!} \textbf{joins!} \textit{ourf!} $only$! \textsc{mission!}

(3) \textit{stuff}\/! \emph{that}\/! \textbf{joins}\/! \textit{ourf}\/! $only$! \textsc{mission}\/!

(4) \textit{stuff}! \emph{that}! \textbf{joins}! \textit{ourf}! $only$! \textsc{mission}!

(5) \textit{stuff!} \emph{that!} \textbf{joins!} \textit{ourf!} $only$! \textsc{mission!}

(6) {\it stuff}! {\em that}! {\bf joins}! {\it ourf}! $only$! {\sc mission}!

(7) {\it stuff!} {\em that!} {\bf joins!} {\it ourf!} $only$! {\sc mission!}

\vspace{12pt}

(1) \textit{stuff}? \emph{that}? \textbf{joins}? \textit{ourf}? $only$? \textsc{mission}?

(2) \textit{stuff?} \emph{that?} \textbf{joins?} \textit{ourf?} $only$? \textsc{mission?}

(3) \textit{stuff}\/? \emph{that}\/? \textbf{joins}\/? \textit{ourf}\/? $only$? \textsc{mission}\/?

(4) \textit{stuff}? \emph{that}? \textbf{joins}? \textit{ourf}? $only$? \textsc{mission}?

(5) \textit{stuff?} \emph{that?} \textbf{joins?} \textit{ourf?} $only$? \textsc{mission?}

(6) {\it stuff}? {\em that}? {\bf joins}? {\it ourf}? $only$? {\sc mission}?

(7) {\it stuff?} {\em that?} {\bf joins?} {\it ourf?} $only$? {\sc mission?}

\vspace{12pt}

(1) \textit{stuff}: \emph{that}: \textbf{joins}: \textit{ourf}: $only$: \textsc{mission}:

(2) \textit{stuff:} \emph{that:} \textbf{joins:} \textit{ourf:} $only$: \textsc{mission:}

(3) \textit{stuff}\/: \emph{that}\/: \textbf{joins}\/: \textit{ourf}\/: $only$: \textsc{mission}\/:

(4) \textit{stuff}: \emph{that}: \textbf{joins}: \textit{ourf}: $only$: \textsc{mission}:

(5) \textit{stuff:} \emph{that:} \textbf{joins:} \textit{ourf:} $only$: \textsc{mission:}

(6) {\it stuff}: {\em that}: {\bf joins}: {\it ourf}: $only$: {\sc mission}:

(7) {\it stuff:} {\em that:} {\bf joins:} {\it ourf:} $only$: {\sc mission:}

\vspace{12pt}

(1) \textit{stuff}/ \emph{that}/ \textbf{joins}/ \textit{ourf}/ $only$/ \textsc{mission}/

(2) \textit{stuff/} \emph{that/} \textbf{joins/} \textit{ourf/} $only$/ \textsc{mission/}

(3) \textit{stuff}\// \emph{that}\// \textbf{joins}\// \textit{ourf}\// $only$/ \textsc{mission}\//

(4) \textit{stuff}/ \emph{that}/ \textbf{joins}/ \textit{ourf}/ $only$/ \textsc{mission}/

(5) \textit{stuff/} \emph{that/} \textbf{joins/} \textit{ourf/} $only$/ \textsc{mission/}

(6) {\it stuff}/ {\em that}/ {\bf joins}/ {\it ourf}/ $only$/ {\sc mission}/

(7) {\it stuff/} {\em that/} {\bf joins/} {\it ourf/} $only$/ {\sc mission/}

\vspace{12pt}

(1) \textit{stuff}- \emph{that}- \textbf{joins}- \textit{ourf}- $only$- \textsc{mission}-

(2) \textit{stuff-} \emph{that-} \textbf{joins-} \textit{ourf-} $only$- \textsc{mission-}

(3) \textit{stuff}\/- \emph{that}\/- \textbf{joins}\/- \textit{ourf}\/- $only$- \textsc{mission}\/-

(4) \textit{stuff}- \emph{that}- \textbf{joins}- \textit{ourf}- $only$- \textsc{mission}-

(5) \textit{stuff-} \emph{that-} \textbf{joins-} \textit{ourf-} $only$- \textsc{mission-}

(6) {\it stuff}- {\em that}- {\bf joins}- {\it ourf}- $only$- {\sc mission}-

(7) {\it stuff-} {\em that-} {\bf joins-} {\it ourf-} $only$- {\sc mission-}

\vspace{12pt}

(1) \textit{stuff}) \emph{that}) \textbf{joins}. \textit{ourf}) $only$) \textsc{mission}.

(2) \textit{stuff)} \emph{that)} \textbf{joins.} \textit{ourf)} $only$) \textsc{mission.}

(3) \textit{stuff}\/) \emph{that}\/) \textbf{joins}\/. \textit{ourf}\/) $only$) \textsc{mission}\/.

(4) \textit{stuff}) \emph{that}) \textbf{joins}) \textit{ourf}) $only$) \textsc{mission}.

(5) \textit{stuff)} \emph{that)} \textbf{joins)} \textit{ourf)} $only$) \textsc{mission)}

(6) {\it stuff}) {\em that}) {\bf joins}) {\it ourf}) $only$) {\sc mission})

(7) {\it stuff)} {\em that)} {\bf joins)} {\it ourf)} $only$) {\sc mission)}

\vspace{12pt}

versus stuff. that. is. not. $an$. issue. I. don't. think $at$. all.


\eqref{eq} no matter what this will \eqref{eq} produce a small difference in the pdf \eqref{eq} wait it's only for ones which end on a line or \eqref{eq}
start on a line? \eqref{eq} what is the pattern \eqref{eq} here exactly \eqref{eq} like I really \eqref{eq} don't see it\dots.

\eqref{eq} that's weird...

\begin{thm}
  \eqref{eq} no matter what this will \eqref{eq} produce a small difference in the pdf \eqref{eq} wait it's only for ones which end on a line or \eqref{eq}
start on a line? \eqref{eq} what is the pattern \eqref{eq} here exactly \eqref{eq} like I really \eqref{eq} don't see it\dots.

\eqref{eq} that's weird...
\end{thm}


\end{document}
